---
title: "Toronto Ice Rink Pads Categorized Based on Total Area"
author: "Enoch Won"
format: pdf
date: "January 24, 2024"
editor: visual
---
```{r}
setwd("C:/Users/enoch/OneDrive/Desktop/STA302/Term Paper 1/inputs/data")
```

Abstract
  This paper uses the data set of indoor ice rink pads in arenas and recreational community centers across Toronto from City of Toronto Open Database. Based on the analysis of the dimensions of ice pads and the different pad size category, a relevantly high discrepancy was observed across different ice pads. There is a positive correlation between ice pad length and width (with the exception of an outlier), which supports the hypothesis that different categories of ice pads have a larger overall area, rather than it being solely larger in length or width. 

All analyses were performed using R Statistical Software(v4.3.2)

Data
The data set is sourced from the City of Toronto Open Data, and the variables that we focus on are "Pad Length", "Pad Width", and "Ice Pad Size Category" to form our analysis. The summary statistics show the mean, median, max, min, and quartiles of the pad length and pad width. 
```{r}
#| echo: false
library(dplyr)
library(readr)
library(opendatatoronto)
library(knitr)
library(ggplot2)

unedited_data <- read_csv("unedited_data.csv")
data <- na.omit(unedited_data)

# Summary Statistics (Mean, Median, Max, Min, etc.)
summary_stats <- summary(data)
print(summary_stats)

# Variance of Pad Length and Pad Width
variable6 <- "Pad Length"
variable7 <- "Pad Width"

#Bar Plot of Ice Rink Pad Size Category
variable9 <- "Ice Pad Size Category"
barplot(table(data[[variable9]]), main = paste("Bar Plot of", variable9), xlab = variable9, cex.names = 0.5, ylab = "Frequency", ylim = c(0, 30), xlim = c(0, 5), col = "pink", border = "black")

#Scatter Plot of Pad Length and Width
plot(data[[variable6]], data[[variable7]], main = paste("Scatter Plot of", variable6, "vs", variable7), xlab = variable6, ylab = variable7, xlim = c(75, 200), ylim = c(69, 100), pch = 15, col = "lightblue")
```

Results
The analysis shows that there is slight variance among pad dimensions, and the graph shows thaat there is a slight positive correlation between "Pad Length" and "Pad Width". There is an outlier, which has a very short pad length, but a very wide pad width. This is the case for an International pad size, in which the dimensions of the ice rink pad is drastically different than any other regulation size. 

References

Parks, Forestry, and Recreation. (n.d.). Open data dataset. City of Toronto Open Data Portal. <https://open.toronto.ca/dataset/indoor-ice-rinks/>.

R Core Team (2023). *R: A Language and Environment for Statistical Computing*. R Foundation for Statistical Computing, Vienna, Austria. <https://www.R-project.org/>.

```{r}

```
